---
title: "Appalachians LANDFIRE Demo"
author: "Randy Swaty with substantial code contributions from Myles Walimaa"
---

<font size="4"> 
**These LANDFIRE-Powered Landscape Assessments allow users to start exploring trends, landscape conversion and natural resource management options. **

</font> 


## Goals of this demonstration

We will use [LANDFIRE](https://landfire.gov/){target="blank"} products to:

1. Characterize and map past and present ecosystem conditions.
2. Explore historical disturbance patterns.
3. Develop R-based processing and visualization


The following charts, maps, and graphs are based on current LANDFIRE products, and provide a starting point for further analysis.




## Location of this demonstration

<br>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}

library(foreign)
library(sf)
library(terra)
library(tidyverse)
library(raster)


```


```{r read shapefile, message=FALSE, warning=FALSE, include=FALSE}
#  read shape
dnbf <- st_read("inputs/dbnf_hex_l5.shp") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf()


edge <- st_read("inputs/edge_hex_l5.shp") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf()



```

```{r locator map, message=FALSE, warning=FALSE, echo=FALSE}
library(tmap)

# toggle tmap mode to interactive viewing
tmap_mode("view")

# create a quick interactive map
quickmap <- tm_shape(dnbf) +
            tm_borders(col = 'darkgreen') +
            tm_shape(edge) +
            tm_borders( col = "blue") +
            tm_layout(title = 'Apps demo landscapes, Edge (blue) and Daniel Boone Nf (green)')



quickmap




```

## How to use this web report

* All maps, input datasets and further assistance can be obtained by contacting the author, [Randy Swaty](mailto:rswaty@tnc.org){target="blank"}.
* Review is ongoing.
* To share this web app, simply share the hyperlink.
* Toggle between dark and light display of this site in the upper right corner of the page.
* Learn more about LANDFIRE and The Nature Conservancy [here](about.qmd){target="blank}. 
